---
title: "Data Scraper"
author: "Samuel Younkin"
date: "Thu 14 May 2015 02:23:09 PM CDT"
output: html_document
---

## Diagnostics for DataScraper Package

### Distribution of Average Heat and Electricity

First we load the DataScraper package and load the energy and property
files.
    
```{r load, echo = TRUE, message = FALSE}
date()
library("DataScraper")
energy <- read.csv(file="./data/energyTables/energyFile-2015-06-06-09-31-08.csv")
property <- read.csv(file="./data/energyTables/Assessor_Property_Information.csv")
data <- merge(energy, property, by.x="parcel", by.y="Parcel")
```

```{r reformat, echo = FALSE}
data <- within(data,{
    Current.Year.Total.Value=as.numeric(gsub("\\$","",as.character(data[,"Current.Year.Total.Value"])))
})
```

```{r table}
table(rowSums(is.na(data[,2:17])))
```

#### MGE Heat Usage Histogram with Outliers Removed

```{r figure2, echo = FALSE, fig.width = 5}
outlierIndex <- which(isOutlier(data[,"therms.3"]))
hist((data[-outlierIndex,"therms.3"]),xlab="Average therms", breaks = 40, main = "Heat Usage (Outliers Removed)")
```

#### MGE Electricity Usage Histogram with Outliers Removed
```{r figure2b, echo = FALSE, fig.width = 5}
outlierIndex <- which(isOutlier(data[,"kWh.3"]))
hist((data[-outlierIndex,"kWh.3"]),xlab="Average kWh", breaks = 40, main = "Electricity Usage (Outliers Removed)")
```

```{r figure3, echo = FALSE, fig.width = 5, eval = FALSE}
outlierIndex <- which(isOutlier(data[,"Current.Year.Total.Value"]))
hist((data[-outlierIndex,"Current.Year.Total.Value"]),xlab="Total Property Value", breaks = 30, main = "Total Property Value (Outliers Removed)")
```

### Lots of outliers

```{r outliers}
sum(isOutlier(data[,"therms.3"]))
sum(isOutlier(data[,"kWh.3"]))
nrow(data)
```

#### The function `isOutlier`

Here is the function `isOutlier`.  An observation must be
greater than one and a half IQRs from the first or third quantile to
be classified an outlier.

```{r isOutlier}
isOutlier
```

#### Session Info

```{r sessionInfo}
sessionInfo()
```

```{r houses, echo = FALSE, eval = FALSE}
head(
  data[
    order(data[,"Current.Year.Total.Value"],decreasing = TRUE),
    c("Address","Current.Year.Total.Value")
  ]
,10)
```
