<link href="http://kevinburke.bitbucket.org/markdowncss/markdown.css" rel="stylesheet"></link>
<link href="http://www.biostat.wisc.edu/~syounkin/markdown_modified.css" rel="stylesheet"></link>

# DataScraper

## Load Libraries

```{r DataScraper, message=FALSE}
library("DataScraper")
library("XML")
require("parallel")
getwd()
date()
```

### Import Assessor Property Information for Madison

```{r input, eval = TRUE}
prop_info <- read.csv(file = "./data/energyTables/Assessor_Property_Information.csv", header=T, sep = ",", stringsAsFactors = FALSE)
```

####  Expand Address field to be multiple fields

Here we use a function written by Tedward to parse the property file.

```{r expand}
prop_info_expandedAddress <- cbind(prop_info, expand_address(prop_info$Address))
```

####  Keep only residential, single unit, single family properties

```{r non-residential}
prop_info_expandedAddress <- subset(prop_info_expandedAddress,
  Property.Class == "Residential" & Dwelling.Units == 1 & Property.Use == "Single family"
)
```

### Retrieve energy data

```{r mge}
timestamp <- gsub("\\s|:","-",Sys.time())
date()
```

```{r mge2}
Active_Address_List <- prop_info_expandedAddress
energy.table.list <- retrieveEnergyList(Active_Address_List, mc.cores = 6)
```

```{r save}
date()
saveRDS(energy.table.list, file = paste("./data/energyTables/energyTableList-", timestamp, ".rds", sep = ""))
```

### Parse data object

Here we take the raw data from the web-server and transform it to a
more manageable form.  We do so using mclapply and take advatage of
multiple cores.

```{r test2, error = FALSE, warning = FALSE}
parsedEnergyList <- mclapply(energy.table.list, parseEnergyTable, mc.cores = 6)
```

### Failures have NULL entries (with length equal to zero)

Calculate the success rate.

```{r failed}
failureIndex <- which(unlist(lapply(parsedEnergyList,function(x)length(x)==0)))
1 - length(failureIndex)/length(parsedEnergyList)
```

### Write parsed data to file

Now we reshape the parsed enegry list to a data frame and write the
data to a ".csv" file.

```{r energyFile}
energy.df <- reshapeEnergyTableList(parsedEnergyList, filename = paste("./data/energyTables/energyFile-",timestamp,".csv",sep=""))
```

### Merge results to property data with "parcel" number

It's easy to merge the energy usage data with the property info.

```{r merge}
dataFull <- merge(energy.df, prop_info, by.x="parcel", by.y="Parcel")
dataFull[1,1:20]
```

### Session Info

What version of R and R packages were used?  We list that here.

```{r session}
sessionInfo()
```
