<<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Primary DataScraper Vignette}
-->

<link href="http://kevinburke.bitbucket.org/markdowncss/markdown.css" rel="stylesheet"></link>
<link href="http://www.biostat.wisc.edu/~syounkin/markdown_modified.css" rel="stylesheet"></link>

# DataScraper: an R package for simulating reads in RNA-seq experiments

## Introduction

```{r DataScraper, message=FALSE}
library("DataScraper")
library("dplyr")
library("XML")
getwd()
date()
set.seed(1)
```

### Importing Assessor Property Information for Madison

```{r input, eval = TRUE}
prop_info<-read.csv(file = "./data/Assessor_Property_Information.csv", header=T, sep = ",", stringsAsFactors = FALSE)
# prop_info[] <- lapply(prop_info, as.character)  # make variables characters, not factors
prop_info<-tbl_df(prop_info)
```

```{r summary}
colnames(prop_info)
table(as.character(lapply(prop_info, class)))
```

###  Expand Address field to be multiple fields
```{r expand}
prop_info_expandedAddress <- expand_address(prop_info$Address)
names(prop_info_expandedAddress)
lapply(prop_info_expandedAddress, class)
```

Note that expand_address returns factors, not characters.  This could
cause bugs down the road.

```{r cat}
prop_info_expandedAddress<-cbind(prop_info,prop_info_expandedAddress)
```

```{r summary2, eval = FALSE, echo = FALSE}
class(prop_info_expandedAddress)
names(prop_info_expandedAddress)
lapply(prop_info_expandedAddress, class)
```

###  Remove non residential property classes from the table


```{r non-residential}
prop_info_expandedAddress <- subset(prop_info_expandedAddress, Property.Class == "Residential")
table(prop_info_expandedAddress$Property.Class)
nrow(prop_info_expandedAddress)
```

```{r non-residential-old, eval = FALSE, echo = FALSE}
prop_info_expandedAddress<-prop_info_expandedAddress %>%
  filter(Property.Class == "Residential")
```

###  Remove  property with zero dwelling units

```{r zero-dwelling, eval = TRUE}
prop_info_expandedAddress <- subset(prop_info_expandedAddress, Dwelling.Units > 0)
table(prop_info_expandedAddress$Dwelling.Units)
nrow(prop_info_expandedAddress)
```

```{r zero-dwelling-old, eval = FALSE, echo = FALSE}
prop_info_expandedAddress<-prop_info_expandedAddress %>%
  filter(Dwelling.Units > 0)
```

What is Active_Address_List?

```{r sgy}
Active_Address_List <- prop_info_expandedAddress
root_url <- "http://www.mge.com/customer-service/home/average-use-cost/results.htm?"

date()

for( i in 1:nrow(Active_Address_List) ){

  house_number<-Active_Address_List$Address_Num[i]   # set house number
  street_direction<-Active_Address_List$Address_StreetDirection[i]   #set sd
  street_name<-Active_Address_List$Address_StreetName[i]   #set street name
  street_suffix<-Active_Address_List$Address_StreetType[i]   #set street suffix/Type
  apartment_unit<-Active_Address_List$Address_UnitNum[i]   #set au
  city<-"Madison"
  
  (full_mge_url<-paste(sep="",root_url,"hn=",house_number,"&sd=",street_direction,"&sn=",street_name,"&ss=",street_suffix,"&au=",apartment_unit,"&c=",city))

  energy_table <- try(readHTMLTable(full_mge_url,as.data.frame=F), silent=TRUE)

  energy.table.list <- c(energy.table.list, energy_table)

}

saveRDS(energy.table.list, file = "./data/energy.table.list.rds")

date()

```

```{r show}
energy.table.list[[1]]
length(energy.table.list)
```

```{r session}
sessionInfo()
```

### Appendix
#### Setting base variables, data frames etc.

Where is "Active_Address_List" defined?

```{r main, eval = FALSE}

### set the root url
root_url<-"http://www.mge.com/customer-service/home/average-use-cost/results.htm?"


### create the output energy table comma separated file
energy_table_column_headers<-c("therms_in_highest_billing_period","gas_cost_in_highest_billing_period","number_days_in_highest_gas_billing_period","therms_in_lowest_billing_period","gas_cost_in_lowest_billing_period","number_days_in_lowest_gas_billing_period","therms_monthly_average","gas_cost_monthly_average","number_days_monthly_average","gas_used_for_heating","kilowatthours_in_highest_billing_period","electric_cost_in_highest_billing_period","number_days_in_highest_electric_billing_period","kilowatthours_in_lowest_billing_period","electric_cost_in_lowest_billing_period","number_days_in_lowest_electric_billing_period","kilowatthours_monthly_average","electric_cost_monthly_average","number_days_monthly_average","electric_used_for_heating","Date_Scraped","Time_Scraped",colnames(Active_Address_List))
energy_table<-formatted_energy_table<-data.frame(matrix(NA,nrow=0,ncol=length(energy_table_column_headers)))
colnames(energy_table)<-energy_table_column_headers
write.table(energy_table, file = "Energy_Table.csv", sep = ",")

### The loop to output a csv
for (i in 61135:63000) {
  ### prepping the URL
  house_number<-Active_Address_List$Address_Num[i]   # set house number
  street_direction<-Active_Address_List$Address_StreetDirection[i]   #set sd
  street_name<-Active_Address_List$Address_StreetName[i]   #set street name
  street_suffix<-Active_Address_List$Address_StreetType[i]   #set street suffix/Type
  apartment_unit<-Active_Address_List$Address_UnitNum[i]   #set au
  city<-"Madison"
  ###combine to create full url
  full_mge_url<-paste(sep="",root_url,"hn=",house_number,"&sd=",street_direction,"&sn=",street_name,"&ss=",street_suffix,"&au=",apartment_unit,"&c=",city)
  
  #test if the webpage exists
  energy_table <- try(readHTMLTable(full_mge_url,as.data.frame=F), silent=TRUE) 
    if ('try-error' %in% class(energy_table)) {
      energy_table<-data.frame(matrix(NA,nrow = 1,ncol = 107))
    } else {
    ### extracting the table from the webpage
    energy_table<-reshape_EnergyUseTable(energy_table)
    energy_table[1,21]<-as.Date(Sys.Date())
    energy_table[1,22]<-Sys.time()
    #### I should also extract the address as it is on their website to check if it is the same as the address I entered.
  }
  energy_table[1,23:(23+length(Active_Address_List[i,]))]<-Active_Address_List[i,]
  if (i == 1){
    write.table(energy_table, file = "Energy_Table.csv", sep = ",", col.names = FALSE, append=FALSE,row.names = F)
  } else {
    write.table(energy_table, file = "Energy_Table.csv", sep = ",", col.names = FALSE, append=TRUE,row.names = F)
  }
  print(i)
  flush.console()
  ##### suspend execution of for loop for seconds #####
  Sys.sleep(runif(1,min = 0,max=10))
}





#erase the energy csv
write.table(file = "Energy_Table.csv", sep = ",", col.names = FALSE, append=FALSE,row.names = F)
```
